---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# jplots

<!-- badges: start -->
<!-- badges: end -->

The goal of jplots is to provide some custom plot functions.

## Installation

You can install the development version of jplots from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jameelalsalam/jplots")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
suppressPackageStartupMessages(library(ggplot2))
library(jplots)

ggplot(ei_ex,
       aes(x = vos,
           y = ei,
           fill = naics)) +
  geom_area_bar(color = "black")
```

This version uses the `envelope_fig` function which constructs the entire plot:

```{r}

envelope_fig(aeo_ex, xname = year, yname = emissions, 
             groupname = scenario, 
             facetname = fuel)

```

However, this approach is not as flexible as using the official ggplot2 extension approach. The following approach extends `geom_ribbon` with a new function `geom_envelope` that calculates the minimum/maximum at each value of `y` and draws an envelope around that range.

```{r}

ggplot(aeo_ex,
       mapping = aes(x = year,
                     y = emissions)) +
  facet_grid(. ~ fuel) +
  geom_line(aes(group = scenario), 
            color = "light blue") +
  geom_envelope(aes(fill = fuel))

```

This approach allows re-mixing the geometry in different ways, e.g., without the facetting:

```{r}
ggplot(aeo_ex,
       mapping = aes(x = year,
                     y = emissions)) +
  geom_line(aes(group = interaction(fuel, scenario)), 
                color = "light blue") +
  geom_envelope(aes(fill = fuel, group = fuel))
```

One important detail: the line geom and the envelope geom have different groupings, so the group aesthetic will have to be specified in one or both geoms. The `interaction` function is useful to group by the interaction of two variables on the fly.

